### 2021-02-25 rad-icfp-2021/relwork.tex
minor
outline paper in intro
adding a ref

\section{Conclusion}

@@

@@

Relatively recent work in AD (2008-2020):
\cite{mak2020differential,elliotthigher,vytiniotis2019differentiable,innes2018don,baydin2017automatic,huot2020correctness,gallagher-sdg,manzyuk2012confusion,wang2018demystifying,beck1994if,wang2018backpropagation,betancourt2018geometric,elliott2018simple,carpenter2015stan,paszke2017automatic,shaikhha2019efficient,innes2019zygote,griewank2008evaluating,kucukelbir2017automatic,brunel2019backpropagation,barthe2020versatility,abadi2019simple,cockett2019reverse,van2018automatic,hascoet2013tapenade,abadi2016tensorflow,pearlmutter2008reverse,bergstra2010theano,fong2019backprop,ehrhard2003differential,agrawal2019tensorflow,bettencourt2019taylor,cruttwell2017cartesian,manzyuk2012simply,laue2018computing}

@@

\noindent \textbf{Limitations.}
\begin{itemize}
    \item memory access for cost function 
    \item parallelism
    \item dedicated tensors for ML, and BLaS considerations
    \item implementation and benchmark
    \item conditionals
    \item recursion
    \item general HO function
    \item more 2nd order functions, though can be derived by hand once and then it's ok
    \item dynamic arrays
    \item more dynamic control flow
    \item all store vs all recompute reverse-mode, and advanced checkpointing
    \item numerical accuracy
    \item fancier types and datatypes (eg dependent, adt) 
    \item iterated ad and higher derivatives
    \item use in Probabilistic programming
    \item non smooth and partial functions, although by simply following the ref book it's as usual in AD
    \item sparsity
    \item other optimisations like implicit function theorem
\end{itemize}

>>>>

\section{Conclusion}
\label{sec:conclusion}

@@

We have shown how to compute provably efficient gradients via reverse derivatives in a purely functional way 
on a simple yet expressive language with array functions.
We introduced a novel intermediate representation, unary form, 
and used it combined with standard functional optimisations to perform our reverse-mode transformation.

@@

Relatively recent work in AD (2008-2020):
\cite{mak2020differential,elliotthigher,vytiniotis2019differentiable,innes2018don,baydin2017automatic,huot2020correctness,gallagher-sdg,manzyuk2012confusion,wang2018demystifying,beck1994if,wang2018backpropagation,betancourt2018geometric,elliott2018simple,carpenter2015stan,paszke2017automatic,shaikhha2019efficient,innes2019zygote,griewank2008evaluating,kucukelbir2017automatic,brunel2019backpropagation,barthe2020versatility,abadi2019simple,cockett2019reverse,van2018automatic,hascoet2013tapenade,abadi2016tensorflow,pearlmutter2008reverse,bergstra2010theano,fong2019backprop,ehrhard2003differential,agrawal2019tensorflow,bettencourt2019taylor,cruttwell2017cartesian,manzyuk2012simply,laue2018computing,bernstein2020differentiating}

@@

\noindent \textbf{Limitations.}
\begin{itemize}
    \item memory access for cost function 
    \item parallelism
    \item dedicated tensors for ML, and BLaS considerations
    \item implementation and benchmark
    \item conditionals
    \item recursion
    \item general HO function
    \item more 2nd order functions, though can be derived by hand once and then it's ok
    \item more dynamic arrays
    \item more dynamic control flow
    \item all store vs all recompute reverse-mode, and advanced checkpointing
    \item numerical accuracy
    \item fancier types and datatypes (eg dependent, adt) 
    \item iterated ad and higher derivatives
    \item use in Probabilistic programming
    \item non smooth and partial functions, although by simply following the ref book it's as usual in AD
    \item sparsity and data manipulation
    \item other optimisations like implicit function theorem
\end{itemize}
